\documentclass[6pt]{article}

\usepackage[none]{hyphenat}
\usepackage{titlesec}
\usepackage{enumitem}
\pagenumbering{gobble}

\titlespacing*{\section}{0pt}{0.0\baselineskip}{\baselineskip}
\addtolength{\topmargin}{-9em}
\addtolength{\oddsidemargin}{-8em}
\addtolength{\evensidemargin}{-8em}

\titleformat*{\section}{\tiny}
\textheight=65em

\titlespacing{\section}{0pt}{2ex}{1ex}
\titlespacing{\subsection}{0pt}{1ex}{0ex}
\titlespacing{\subsubsection}{0pt}{0.5ex}{0ex}

\setlist[itemize]{leftmargin=*}

\begin{document}
%
% Start of "Personal Details" section (sidebar)
%
\hspace*{-\parindent}%
\begin{minipage}{15em}
\textheight=65em
\section*{}
{\fontfamily{qhv}\selectfont \underline{\textbf{Personal Details}}}
\break

{\small {\bfseries Website} -- https://www.ekn.io

{\bfseries Github} -- eriknyquist

{\bfseries Email} -- eknyquist@gmail.com}

\section*{}
{\fontfamily{qhv}\selectfont \underline{\textbf{Areas of Expertise}}}
\subsection*{}
{\textbf{Programming Languages}}

{\small C

C++

C\#

Python

UNIX shell scripting (bash, sh)}

\subsection*{}
{\textbf{Tools \& Environments}}

{\small Git

GCC/Clang

Makefiles

GNU ld (linker) scripting

Google Protocol Buffers

GDB

OpenOCD

Valgrind

{\LaTeX}

Eclipse

Jenkins

JIRA

Unity/CMock}

\subsection*{}
{\fontfamily{qhv}\selectfont \underline{\textbf{Personal Skills}}}

\noindent
\begin{itemize}
{\small \raggedright
    \item Test-driven development
    \item Fault finding and debugging on embedded systems
    \item C and C++ for memory constrained embedded systems
    \item Rapid prototyping/testing with Python or UNIX shell scripting
}
\end{itemize}

\subsection*{}
{\fontfamily{qhv}\selectfont \underline{\textbf{Interests}}}

\noindent
\begin{itemize}
{\small \raggedright
    \item Compiler design and implementation
    \item Programming language design and implementation
    \item Playing music (drums, piano)
}
\end{itemize}
\end{minipage}
%
% Start of main section (page 1)
%
\begin{minipage}{35em}
%
% Document title
%
{\fontfamily{qhv}\selectfont \Huge \bfseries Erik Nyquist}
{\hfill \today}
\section*{}

An enthusiastic and skillful software engineer, with a comprehensive knowledge of
development and validation practices for embedded software systems. Accustomed to
delivering and enforcing high quality code and documentation in a high-pressure
environment.

\section*{}
{\fontfamily{qhv}\selectfont \Large \bfseries Experience}

\titlerule
%
% Current job
%
\subsection*{}
\begin{minipage}{20em}
{\bfseries Firmware Engineer, NOVO Engineering

Vista, CA}
\end{minipage}
\hfill
\begin{minipage}{10em}
{\bfseries Aug. 2017 - present}
\end{minipage}
\break
\break
Designing and developing low-level firmware and user-level software for embedded
systems (Linux, FreeRTOS)
\begin{itemize}
    \item Developed firmware for multiple medical device products using nRF SoCs
          (closed loop insulin delivery system, "smart" insulin pen cap)
    \item Developed firmware for multiple pieces of test equipment for medical
          device products using nRF SoCs
    \item Developed automated unit tests and integration tests (Python, C) for
          multiple medical device products
    \item Participated in creation of product verification documentation for
          multiple medical device products
\end{itemize}
\dotfill

%
% Previous job
%
\subsection*{}
\begin{minipage}{20em}
{\bfseries Software Engineer, Intel

San Diego, CA}
\end{minipage}
\hfill
\begin{minipage}{12em}
{\bfseries Aug. 2016 - Aug. 2017}
\end{minipage}
\break
\break
Developed low-level hardware drivers and firmware for Intel's low-power SoC products
with a small team, including Intel's Galileo, Joule and Curie modules (Linux, RTOS and
bare-metal).
\begin{itemize}
    \item Developed drivers and firmware (C, C++) for the Intel Arduino 101 board, using the
          open-source Zephyr project (co-operative scheduling real-time kernel for small
          embedded systems. www.github.com/01org/zephyr).
    \item Developed Arduino user libraries and APIs (C, C++) for the Intel Arduino 101 board,
          reviewed/accepted patches from public users regularly \\
          (www.github.com/01org/corelibs-arduino101).
    \item Developed drivers and developer tutorials (C++) for the Pattern Matching Accelerator
          on the Quark SE C1000 microcontroller (on-die network of 128 hardware neurons
          capable of autonomous learning/training, and pattern recognition.
          www.github.com/01org/Intel-Pattern-Matching-Technology).
    \item Participated in design and development of the Curie Open Developer Kit (C, C++,
          bash/shell, OpenOCD, GDB), a lightweight framework for developing applications
          (bare-metal, or using the Zephyr kernel) that can fully utilize the two asynchronous
          CPU cores on an Intel Curie device (www.intel.com/curieodk).
\end{itemize}
\end{minipage}
%
% Start of main section (page 2)
%
\hspace{2em}
\begin{minipage}{50em}
\dotfill

%
% Previous job
%
\subsection*{}
\begin{minipage}{20em}
{\bfseries SoC Software Engineer, Intel

San Diego, CA}

\end{minipage}
\hfill
\begin{minipage}{28em}
{\bfseries \hfill Sep. 2014 - Apr. 2016}
\end{minipage}
\break
\break
Developed and tested low-level hardware drivers and firmware for Quark SoCs (Linux and bare-
metal).
\begin{itemize}
    \item Developed Linux-based test suites (C, Python), for various embedded protocols and
          systems (UART, CAN, I2C, SPI), on FPGA-emulated systems and during new device
          bring-up/power-on.
    \item Developed test suites (C, Python) for customer SW tools (tools for writing BIOS
          configuration data to an EEPROM/flash device on a customer board, tools for
          generating a bootable OS image with custom BIOS, kernel and root filesystem parts)
    \item Functional testing of customer SW tools \& platforms (microcontroller I/O libraries, toolchain,
          debugging tools).
    \item Low-level debugging and fault-finding (source and assembly level debug with OpenOCD and GDB,
          analyzing linker scripts, linker map files, and looking at scope traces / logic analyzer traces, to
          debug I/O device drivers or C/C++ run-time init. code running on a target microcontroller device)
\end{itemize}
\dotfill

%
% Previous job
%
\subsection*{}
\begin{minipage}{20em}
{\bfseries Software Design Engineer, Intel

Ireland}

\end{minipage}
\hfill
\begin{minipage}{14em}
{\bfseries \hfill Aug. 2012 - Sept. 2014}
\end{minipage}
\break
\break
Developed and tested Linux-based software \& drivers for the Intel Quark X1000 SoC. Brought Intel
Galileo board (first x86-based Arduino board) from design to market.
\begin{itemize}
    \item Prototyped software solutions for supporting Arduino-compatible code on an embedded linux-
          based platform
    \item Usability and functional testing of customer SW tools (Code editor/IDE, setup tools and scripts)
    \item Provided technical support to users via online forum www.maker.intel.com
\end{itemize}

\section*{}
{\fontfamily{qhv}\selectfont \Large \bfseries Education}

\titlerule
\subsection*{}
{\bfseries Master of Science, Computer Science}

University College Dublin, Belfield, Ireland
\subsection*{}
{\bfseries Bachelor of Engineering, Audio Visual Media Technology}

Dun Laoghaire Institute of Art, Design and Technology, Dublin, Ireland

\end{minipage}
\end{document}
